---
title: "unc-104_vs_control_plot"
output: html_notebook
---
```{r}
#libraries used in this notebook
library(gmodels)
library(ggplot2)
library(qqplotr)
library(dplyr)
library(tidyverse)
library(ggpubr)
library(here)
#reads in the dataframe
dat <-read.csv(here("datafolder", "unc-104_data.csv"))
factorNames <- c("control","unc-104(e1265)") #defines the genotypes to be analyzed 
mat_dat_104 <- filter(dat, genotype %in% factorNames) #filters only the factors (genotypes) to be analyzed
mat_dat_104$genotype <- factor(mat_dat_104$genotype, levels =c("control","unc-104(e1265)"))

```

```{r}
#organization of the data
#subset the columns that will be used in analysis and renames columns to more readable names
mat_dat_104_red <- select(mat_dat_104,id, genotype, neurite_red, soma_red, cell_red)

mat_dat_104_red
mat_dat_104_red <- mat_dat_104_red %>% 
  rename(Neurite = neurite_red,
         Soma = soma_red,
         Cell = cell_red
    )
mat_dat_104_red
#now for the yellow data
mat_dat_104_yellow <- select(mat_dat_104, id, genotype, neurite_yellow, soma_yellow, cell_yellow)
mat_dat_104_yellow <-mat_dat_104_yellow %>% 
  rename(Neurite = neurite_yellow,
         Soma = soma_yellow,
         Cell = cell_yellow
    )
#pivots the location data for the observations longer. Stores the data values under values column and the old column names under a new column named location.
mat_dat_104_red <-mat_dat_104_red %>%
 pivot_longer(cols = c(Neurite, Soma, Cell),
   names_to = "location",
   values_to = "value")
mat_dat_104_yellow <-mat_dat_104_yellow %>%
 pivot_longer(cols = c(Neurite, Soma, Cell),
   names_to = "location",
   values_to = "value")
#reorders the location factors to aide in graphical representation of data
mat_dat_104_red$location <- factor(mat_dat_104_red$location,
                                    levels = c("Neurite", "Soma", "Cell"))

mat_dat_104_yellow$location <- factor(mat_dat_104_yellow$location,
                                    levels = c("Neurite", "Soma", "Cell"))

```


```{r}
#position jitter function
posn_j <- position_jitter(width=.2)
#dot plot of the red data in the locations of the neuron faceted
mat_104_plot_red <- ggplot(data=mat_dat_104_red, aes(x=genotype, y=value, fill=location)) +
  geom_violin(aes(x=genotype, y=value, fill=location),
              fill = "red",
              alpha = .3,
              draw_quantiles = c(.5))+
  facet_wrap(vars(location))+ #facets the data to show the location in the cell of the red AG's
  geom_point(alpha = 0.6,
             position =posn_j)+ #creates a dotplot of the data
  stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", alpha = .8,  width=0.2, size = .8) + #creates an error bar based on one standard devation of the data
  fig_one_theme+ #loads theme elements from other figures in the manuscript
  coord_cartesian(ylim = c(0,18))+ #creates the limits of the graph
  theme(legend.position = "none")+ #gets rid of legend
  labs(y = "ALs per AIY Neuron")
  #geom_signif(stat="identity"
              #data = data.frame(x=c(.85,.85),
                               # xend=c(2.15,3.15),
                               # y=c(13,15),
                                #annotation=c(""))
              

mat_104_plot_red

#dot plot of the yellow data in the locations of the neuron faceted
mat_104_plot_yellow <- ggplot(data=mat_dat_104_yellow, aes(x=genotype, y=value, fill=location)) +
  geom_violin(aes(x=genotype, y=value, fill=location),
              fill = "yellow",
              alpha = .3,
              draw_quantiles = c(.5))+
  facet_wrap(vars(location))+ #facets the data to show the location in the cell of the red AG's
  geom_point(alpha = 0.6,
             position =posn_j)+ #creates a dotplot of the data
  stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", alpha = .8,  width=0.2, size = .8) + #creates an error bar based on one standard devation of the data
  fig_one_theme+ #loads theme elements from other figures in the manuscript
  coord_cartesian(ylim = c(0,18))+ #creates the limits of the graph
  theme(legend.position = "none")+
  labs(y = "AGs per AIY Neuron")


mat_104_plot_yellow

    
```
```{r}
mat_104_plot_red
mat_104_plot_yellow
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
